\documentclass[11pt]{extarticle} %extarticle for fontsizes other than 10, 11 And 12
%\documentclass[11p]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Input header file 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{HeaderfileTexDocs}

\geometry{left=0.9in, right=0.9in, top=0.9in, bottom=0.9in}

\begin{document}
\doublespacing
%\SweaveOpts{concordance=TRUE}
\bibliographystyle{plain}  %Choose a bibliograhpic style

\title{Effects of Great Recession on Income Poverty}
\author{Subharati Ghosh, Subhrangshu Nandi, Susan Murphy \\
%  Statistics PhD Student, \\
%  Research Assistant,
%  Laboratory of Molecular and Computational Genomics, \\
%  University of Wisconsin - Madison}
%\date{February 16, 2015}
\date{}
}

\maketitle

\section{Study Aim}
The aim of this study is to analyze how households with a working age adult with disability compare with households with no adult with disability, during the {\emph{great recession}}, using ``Income Poverty'' as a measure of economic wellbeing, when controlling for demographic factors such as gender, marital status, education, race and origin. 

\section{Sample}
For this analysis data from US Census Bureau's SIPP 2008 panel survey was used. {\footnote{For more information on the SIPP 2008 panel schedule, please refer to this \href{http://www.census.gov/programs-surveys/sipp/data/2008-panel.html}{US Census Bureau website}}}. Questions on whether the households had a working age adult with disability were asked in wave-6 of the survey, which ended in August, 2010. Households that participated in wave-6 were included in our sample. There were a total of 34,850 households in wave six. Survey data upto wave-15 were used in our sample. Survey results from July, 2008 through June, 2013 were included in the analysis. Households whose reference person remained the same throughout the 2008 panel were kept in the sample. The reference persons of the households were also required to be 18 years or older throughout the 2008 panel. The final sample had 33,547 households that satisfied all the inclusion criteria. 

\section{Methods}
Total monthly household income was divided by monthly federal poverty level (FPL) and then averaged over quarters to estimate FPL100-ratio. An FPL100-ratio lower than one in any quarter indicated the household was below 100\% Federal poverty level in that quarter. Averaging monthly values over a quarter reduced the noise in the response variable by eliminating the month-by-month variability in the income data. In the sample, the monthly income data ranged from -\$27,180 to \$108,900, the average being \$5240 and median \$3,874. The negative incomes were associated with households owning business that incurred lossed in those months. The FPL100-ratio ranged from -17.95 to 89.48, with the average being 3.817 and the median 2.924. In the sample, 7,865 out of 33,547 households (23.44\%) had at least one working age adult with disability during the observed time period, as identified in wave-6 of the survey. Data from July 2008 (2008-Q3) through May 2013 (2013-Q1) were analyzed. This period overlapped with twelve of the eighteen months {\footnote{\href{http://www.nber.org/cycles/}{NBER Recession Cycles}}} of the ``Great recession'' and its long wake. 

\subsection{Mixed-effects model for income poverty}
A mixed (fixed and random) effects model was fit to estimate the impact of the presence of a working-age adult with disability in a household on its FPL100-ratio. Let $Y$ denote the vector or responses (FPL100-ratio). Let $\Theta$ denote the vector of fixed effect factors like gender, marital status, education level, race, origin of household head, along with their interactions. Let $\beta$ denote another fixed effect of time, represented as quarters, starting from 2008-Q3 and ending in 2013-Q1. Let $b$ denote the household level random effect (random intercept). Then, the mixed-effects (\cite{Fitzmaurice_2012_Applied}) model for the responses, for each household $i$ can be written as
\vspace{-0.5cm}
\begin{equation}
Y_{ij} = \beta_0 + \beta t_j + X_i\Theta + b_i + \epsilon_{ij}
\label{eq:MixedEffects1}
\end{equation}
where, $\epsilon_{ij}$ are regarded as measurement errors, $i$ goes from $1$ to $H$, the number of households, $j$ goes from $1$ to $T$, the total number of quarterly observations for every household. In this model, the response from the $i^{th}$ household at time $t_j$ is assumed to differ from the population mean $X_i\Theta + \beta t_j$ by a household effect $b_i$ and a within household measurement error $\epsilon_{ij}$. The within household and between household errors are assumed to be normal and independent ($b_i \sim \N(0, \sigma^2_b),\ \ \epsilon_{ij} \sim \N(0, \sigma^2), \ \ b_i \indep \epsilon_{ij}, \forall i, j$). The effect of ``time'' is a fixed effect and it could be considered part of the fixed effect design matrix $X$. However, the problem of interest is to test a linear hypothesis about the disability-by-time interaction, to detect the effect of disability on the mean response over the period of the study. Hence, the ``time'' covariate is denoted separately. During estimation it will be estimated as a fixed effect. 

The bottom, or trough, of the great recession was reached in the second quarter of 2009 (marking the technical end of the recession, defined as at least two consecutive quarters of declining GDP) \footnote{Business Cycle Dating Committee, National Bureau of Economic Research (NBER)}. According to NBER, June 2009 was the final month of the recession. We wanted to check if this was reflected in the FPL100-ratio as a downward trend in the initial quarters followed by an upward trend. A simple linear term in ``time'' would be insufficient. We added a second order term $\text{time}^2$ to test the change in direction of trend. The second order term was added after centering the original ``time'' variable, to avoid introducing multicollinearity. 

Below is the model that will be fit: 
\vspace{-0.5cm}
\begin{equation}
Y_{ij} = \beta_0 + \beta_1 t_j + \beta_2 t_j^2 + \delta \Ind_{D_i} + \gamma(\Ind_{D_i}*t_j) + X_i\Theta + b_i + \epsilon_{ij}
\label{eq:MixedEffects2}
\end{equation}

where, $\Ind_{D_i} = 1$, if household $i$ has a working age adult with disability, else $\Ind_{D_i} = 0$. The hypotheses of interests are: \\
$H_0: \beta_1 = 0, \text{  vs  } H_a: \beta_1 \ne 0$ tested if FPL100-ratio changed over time \\
$H_0: \beta_2 = 0, \text{  vs  } H_a: \beta_2 \ne 0$ tested if the trend of FPL100-ratio changed direction \\
$H_0: \delta = 0, \text{  vs  } H_a: \delta \ne 0$ tested if disability had any effect on FPL100-ratio\\
$H_0: \gamma = 0, \text{  vs  } H_a: \gamma \ne 0$ tested if disability had any effect on the slope of FPL100-ratio during the study period\\
$H_0: \Theta = 0, \text{  vs  } H_a: \Theta \ne 0$ tested if demographic factors had any effect on FPL100-ratio. \\
In addition, interactions between demographic factors, and between disability and demograhic factors were also tested. 

\noindent
{\bf{Demographic factors}}\\
The demographic factors were considered as fixed effects. The factors included in this analysis were {\emph{gender}}, {\emph{marital status}}, {\emph{education}}, and {\emph{race/origin}} of household head. The {\emph{Race/Origin}} factor included ``non-hispanic white'', ``non-hispanic black'', ``hispanic'' and ``others''. For simplicity, ``white'' and ``black'' would indicate categories ``non-hispanic white'' and ``non-hispanic black''. Gender of household head had two categories: ``male'' and ``female''. Education of household head has three categories: ``high-school or less'', ``some college, diploma, associated degrees'' and ``bachelors or higher''. Marital status of household heads has two categories: ``married'' and ``not married''. Divorced or widowed household heads were considered in the ``not married'' category. 

\noindent
{\bf{Computational software}}\\
All analysis were conducted using the statistical software R (\cite{R}), version 3.3.1. The mixed effects models were fit using the R-package ``lme4'' (\cite{R-lme4}) and all hypothesis tests were done using the R package ``lmerTest'' (\cite{Kuznetsova_etal_2015_R-lmerTest}). The final model was fit with some of the fixed effect factors along with their interactions after performing ``backward elimination'' on the full model. Elimination of the fixed effects were done by the principle of marginality, that is: the highest order interactions are tested first: if they are significant, the lower order effects were included in the model without testing for significance. The p-values for the fixed effects are estimated from the F statistics, with ``Satterthwaite'' approximation (\cite{Satterthwaite_1946_Biometrics}) denominator degrees of freedom. The p-values for the random effect were computed from likelihood ratio tests (\cite{Morrell_1998_Biometrics}). 

\subsection{Model for income poverty, with baseline correction} \label{baselineCorrection}
In order to isolate the effect of the {\emph{great recession}} on income poverty (response), measured by FPL100-ratio, the values of the response at the beginning of study period (2008-Q3) were subtracted from each household's responses. Consequently, all FPL100-ratios of all households at 2008-Q3 were zero. The same model as in eq \ref{eq:MixedEffects1} was fit to this baseline-corrected responses. The problem of interest was to test a linear hypothesis about the disability-by-time interaction. 

\subsection{Post-hoc tests}
Post-hoc tests were conducted between categories of all demographic factors and their interactions, by calculating differences of ``Least Squares Means'' using R package ``lmerTest'' (\cite{Kuznetsova_etal_2015_R-lmerTest}), with ``Satterthwaite'' approximation (\cite{Satterthwaite_1946_Biometrics}) of the denominator degrees of freedom. \\
\noindent
{\bf{Multiple testing correction}}\\
When conducting post-hoc tests for demographic factors and their interactions, due to multiple categories of these factors the size of the tests might be inflated. Sequentially rejective {\emph{Bonferroni procedure}} (\cite{Holm_1979_SJS}) and {\emph{Benjamini-Hochberg procedure}} (\cite{Benjamini_Hochberg_1995_JRSSB}) remain the two most popular multiple testing correction procedures. Holm's sequentially rejective Bonferroni procedure controls the family-wise type-I error rate (FWER) and is more powerful than the classical Bonferroni procedure. Benjamini-Hochberg controls the false discovery rate (FDR) which is the expected value of false discovery proportion. Controlling FWER usually proves to be too conservative. Hence, we used the Benjamini-Hochberg procedure , which is less conservative, but more powerful than Bonferroni correction. All post-hoc test p-values reported are Benjamini-Hochberg corrected.

\section{Results}
Table \ref{tab:FixedEffectsBetas} shows the coefficients of time (measured in year-quarters), and disability and the interaction between them. The first model includes the baseline FPL100-ratio and the second model does not. The rationale for the second model is explained in section \ref{baselineCorrection}. Both these models include the demographic factors. ANOVA tables of these demographic factors are in tables \ref{tab:Anova1} and \ref{tab:Anova2} respectively, for the two models. The coefficients in the two models are comparable. For example, $\beta_{\text{time}} = -0.0515, p < 0.01$ in model 1, indicating, FPL100-ratio decreased by $0.05$ every quarter, during the study period. The coefficient of {\emph{Disability}} is $\beta_D = -30.8394, p < 0.01$ in model 1 indicate that households with a working age adult with disability had their FPL100-ratios $30.84$ lower, on an average, compared to households without any working age adult with disability. Next, we observe that the coefficient of interaction between time and disability ($\beta_{t*D} = 0.0151, p < 0.05$) is positive. This implies that the slope of FPL100-ratio with time for households with disability is $-0.0364 (-0.0515 + 0.0151)$, which is less negative than the households without disability. This apparent contradictory finding leads us to conclude that households with disability although had significantly worse FPL100-ratio throughout the study period, the households without disability experienced more severe declines in their FPL100-ratios. This could throw some light on the impact of different supplementary coverage programs on households with disability. 

Although the coefficients of the two different models (without and with baseline correction) were similar, we feel Model 2 is more appropriate for reasons explained in \ref{baselineCorrection}. For all the demographic factors and for interactions between them, post-hoc tests were conducted to identify the pairwise differences in mean FPL100-ratios of different subgroups. 

\noindent
{\bf{Gender of household head}} \\

\noindent
{\bf{Marital status of household head}} \\

\noindent
{\bf{Race/Origin of household head}} \\
In table \ref{tab:RaceOrigin} we can see that regardless of disability, in Model1, households with a ``black'' ($\mu_{\text{diff}} = -0.53, p = 0.0000$) or ``hispanic'' ($\mu_{\text{diff}} = -0.46, p = 0.0000$) race/origin as household head is worse off compared to those with ``others'' race/origin. The discrepancy is higher between ``black'' and ``white'' household heads ($\mu_{\text{diff}} = -0.90, p = 0.0000$). When corrected for baseline, the relationships reverse in sign, indicating that during the study period, ``black'' and ``hispanic'' households fared marginally better than ``white'' and ``others''. When considering only the households with disability (table \ref{tab:DisabRaceOrigin}), there is no significant difference between the different races. \\
\noindent
{\bf{Education of household head}} \\
In table \ref{tab:Education}, we see that regardless of disability, in Model1, households in ``high school or less'' is worse off than ``some college, diploma'' ($\mu_{\text{diff}} = -0.47, p = 0.0000$), which is in turn worse off than ``bachelors or higher'' ($\mu_{\text{diff}} = -1.29, p = 0.0000$). In Model 2, only the difference between ``some college, diploma'' and ``bachelors or higher'' groups are significant ($\mu_{\text{diff}} = -0.08, p = 0.014$. When considering only the households with disability (table \ref{tab:DisabEducation}), there is no significant difference between the different education groups. \\
\noindent
{\bf{Interaction of Gender and Marital status}} \\
In table \ref{tab:GenderMS}, we see that in Model 1 ``female, not married'' households are worse off than ``male, married'' ($\mu_{\text{diff}} = -0.92, p = 0.0000$), than ``female, married'' ($\mu_{\text{diff}} = -0.75, p = 0.0000$) and ``male, not married'' ($\mu_{\text{diff}} = -0.65, p = 0.0000$). In Model 2, similar relationships hold, with smaller mean difference. Even when considering only the households with disability (table \ref{tab:DisabGenderMS}), the same relationships hold between the groups. We conclude that ``female, not married'' households fared the most poorly through our study period. \\
\noindent
{\bf{Interaction of Gender and Education}} \\
Focusing on the households In table \ref{tab:GenderRaceOrigin}, we see that in Model 1,      \\
\noindent
{\bf{Interaction of Race/Origin and Marital status}} \\
In table \\

\noindent
{\bf{Interaction of Marital status and Education}} \\
In table \\

\noindent
{\bf{Interaction of Race/Origin and Education}} \\
In table \\

\section{Limitations}
\begin{enumerate}
\item Although a linear mixed effects regression model discovered some conventional and some interesting patterns in the relationships between response and demographic factors, along with disability, the trajectory of income poverty over the study period for some households were not linear. This modeling approach does not capture trajectory shapes of individual households. A non-parametric fitting of the income poverty trajectories could be tried as a pre-processing step before testing for differences in behavior between different groups of households. 
\end{enumerate}

\newpage
\input{Tables_IncomePoverty}



\newpage
\bibliography{bibTex_Reference}
\end{document}
